Genome-wide changes in expression during inflorescence architecture development

### 2015-09-04 ms.Rmd
added second cluster table

```{r pander, results = "asis"}
pander::set.alignment('center', row.names = 'right')
pander::set.caption(paste0(
  I(pasteLabel("**Table ", tableCount, "t_hypergeom")),
  "**: Transcription factor and transcriptional regulator family enrichment for families that had at least two members in any one cluster, including the number of family members (*n*), number expressed in the whole dataset (*n*~expr~) and number and adjusted *p*-value for each cluster."))
pander::pandoc.table(t_hypergeom, split.tables = Inf, emphasize.rownames = FALSE)
```

>>>>

```{r t_familiesPerCluster, results = "asis"}

pander::set.caption(paste0(
  I(pasteLabel("**Table ", tableCount, "t_familiesPerCluster")),
  "**: Transcription factor and transcriptional regulator family members in each cluster. *n*, total number of family members, *n*~expr~, number of family members expressed in the whole dataset, C~1~–C~", c, "~, number of family members in each cluster, and the total number of family members in all clusters."))
t_familiesPerCluster <- as.data.frame(t_familiesPerCluster[!Total == 0])
rownames(t_familiesPerCluster) <- t_familiesPerCluster$Family
t_familiesPerCluster$Family <- NULL
pander::pandoc.table(t_familiesPerCluster, split.tables = Inf, emphasize.rownames = FALSE,
                     justify = c("right", rep("centre", length(names(t_familiesPerCluster)) - 1), "left"))

```{r t_hypergeom, results = "asis"}
pander::set.alignment('center', row.names = 'right')
pander::set.caption(paste0(
  I(pasteLabel("**Table ", tableCount, "t_hypergeom")),
  "**: Transcription factor and transcriptional regulator family enrichment for families that had at least two members in any one cluster, including the number of family members (*n*), number expressed in the whole dataset (*n*~expr~) and number and adjusted *p*-value for each cluster."))
pander::pandoc.table(t_hypergeom, split.tables = Inf, emphasize.rownames = FALSE)
```
